\section{Conclusions}\label{sec:conclusions}
We derived an explicit expression for the Jacobian of a finite-difference discretization of the incompressible Navier-Stokes equations. Both the Jacobian of the system of equations and the Jacobian of the related boundary condition was computed exactly. By using the block-structure of the discretization, we showed that the Jacobian had a block structure as well, which lead to a compact and clean expression. We also showed that large parts of the Jacobian were computed by evaluating the discretization.
We showed that the Jacobian could be used both in steady-state and time-dependent simulations. The numerical discretization was verified by manufactured solutions and the spatial convergence rates agreed well with the theoretical expectations. Furthermore, the computed estimates of the iterative convergence rates for Newton's method was two, and verified that the Jacobian was correctly computed.
The methodology used in this paper is general and can be used in a straightforward manner for any numerical discretization of initial boundary value problems that can be written in matrix-vector form.
%has been illustrated for different cases and also verified by the method of manufactured solutions.

%Due to the use of encapsulated difference operators, the extension to a curved grid is straight forward. Different boundary conditions such as the solid wall, the Dirichlet inflow and pressure outflow conditions have been used and the Jacobian for all these sets of boundary conditions were also presented. Lastly, the numerical method has been illustrated for different cases and also verified by the method of manufactured solutions. 
